---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sensataDataProg

<!-- badges: start -->
<!-- badges: end -->


This package is a WIP that has the functions needed to clean and manipulate data created with the Sensata platform.

Este paquete es un WIP que tendrá las funciones necesarias para limpiar y manipular los datos de la plataforma Sensata.

## Installation

It will not be publish on CRAN, you can only install it from [GitHub](https://github.com/) with:

No se va a publicar en CRAN, solo se puede instalar de [GitHub](https://github.com/) con:


``` r
# install.packages("devtools")
devtools::install_github("GaborioSensata/sensataDataProg")
```
## Example

This is a basic example which shows you how to create a dictionary of the microdata:

Este es un ejemplo básico que muestra cómo crear un diccionario de los microdatos:

```{r example, eval=FALSE}
library(sensataDataProg)

diccFunction(dat = pathOfMongoCsvFile, f = pathToSaveDictionaries )

```
