---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sensataDataProg

<!-- badges: start -->
<!-- badges: end -->


This package has the functions needed to clean and manipulate data created with the Sensata platform.

Este paquete tiene las funciones necesarias para limpiar y manipular los datos de la plataforma Sensata.

## Installation

It will not be publish on CRAN, you can only install it from [GitHub](https://github.com/) with a Personal Access Token (create one that expires soon):

No se va a publicar en CRAN, solo se puede instalar de [GitHub](https://github.com/) con un token de acceso personal (PAT):


``` r
# install.packages("devtools")
# Don't run this on a script, only on console so you don't save your PAT in a script:
devtools::install_github("GaborioSensata/sensataDataProg", ref = "main", auth_token = "ENTER_HERE_YOUR_PAT")
```
## Example

This is a basic example which shows how to prepare raw data from sensata platform (data included as an example in the package):

Este es un ejemplo básico que muestra cómo preparar datos raw de la plataforma sensata (datos incluidos como ejemplo en el paquete):

```{r example, eval=FALSE}
library(sensataDataProg)

rawData <- sensataDataProg::sensataExample

Dict <- dictGenerator(
  df = rawData,
  questionPrefix = "",
  forceOrdered = "q_AB_NI_01"
)

Dict$options <- sub("\\//.*", "", Dict$options)


intData <- cleanCols(df = rawData,
                    dictionary = Dict)

intData<- scrubRows(df = intData,
          testParamName = "test")

intData <- intData %>% makeFactors(dictionary = Dict,
                                   multChoiceText = c("Yes", "No"))


```

## TO-DO

- Learn how to use a stored PAT with package credentials
- Create vignettes
